Accelerating Neural Network Training using Arbitrary Precision Approximating Matrix Multiplication Algorithms

### 2021-03-01 latex/MPP21/paper.tex
added hybrid figure

\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{tikz,pgfplots}

@@

\begin{figure}
\input{figs/hybrid}
\caption{Illustration of hybrid parallelization strategy for $r=10$ and 4 threads.}
\label{fig:hybrid}
\end{figure}

>>>>

\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{tikz,pgfplots}
\usetikzlibrary{positioning}

@@

\begin{figure}
\centering
\input{figs/hybrid}
\caption{Illustration of hybrid parallelization strategy for $r=10$ and 4 threads.  Each thread is assigned two multiplications to compute using single-threaded \texttt{gemm} and the two remaining multiplications are performed using multithreaded \texttt{gemm}.}
\label{fig:hybrid}
\end{figure}
